Do investors in clean energy ETFs herd?

### 2025-03-24 alt_energy_herding.qmd
finalising comments

We observe several periods of herding behaviour as reflected in the troughs in @fig-rolling_window. The most prominent cases of herding occur between March and May of 2020 followed by several instances of herding in the period that extends from March through April of 2017 and the period of February-March of 2023. On the other side, we derive significant moments of anti-herding behaviour in the clean energy ETFs by observing the spikes in @fig-rolling_window. Cross sectional dispersion appears to increase with respect to market-wide returns which is a sign of anti-herding behaviour on behalf of investors around December of 2016 and later during September of 2022.

@@

The results from the Probit model are reported in @tbl-probit_analysis, where only the physical risk index significantly decreases the probability of herding.^[It should be noted that due to availability issues the probit analysis ends in December of 2023.] In other words, climate risks is good news for clean energy stocks or firms resulting in anti-herding behaviour. This implies that in the presence of higher physical risk with respect to the climate, clean energy ETFs become a more attractive investment option for investors that allocate their money to the various alternative energy investment products. As a result, the cross-sectional dispersion of clean energy ETFs tends to increase. Our results are in line with those of rrelevant studies such as Gabriel & Pinho (2024) who claimed that in the event of climate policy shocks, clean energy assets could serve the role of hedging instruments.

>>>>

We observe several periods of herding behaviour as reflected in the troughs in @fig-rolling_window. The most prominent cases of herding occur between March and May of 2020 followed by several instances of herding in the period that extends from March through April of 2017 (when $\gamma_2$ averaged -45.5) and the period of February-March of 2023 (when $\gamma_2$ averaged -7.68).We observe significant herding in the onset of the COVID-19 crisis 2020, which was short lived as market adapted. The rest of the Covid period was in the main characterised by anti-herding behaviour. @ghorbel2023 and @dhall2020 found similar results. Lastly, similar to @mohamad2024 we observe no herding behaviour related to the Russia-Ukraine war. @mohamad2024 highlights the importance of context in understanding the link between herding and market events. On the other side, we derive significant moments of anti-herding behaviour in the clean energy ETFs by observing the spikes in @fig-rolling_window. Cross sectional dispersion appears to increase with respect to market-wide returns which is a sign of anti-herding behaviour on behalf of investors around December of 2016 and later during September of 2022.

@@

The results from the Probit model are reported in @tbl-probit_analysis, where only the physical risk index significantly decreases the probability of herding.^[It should be noted that due to availability issues the probit analysis ends in December of 2023.] In other words, climate risks is good news for clean energy stocks or firms resulting in anti-herding behaviour. This implies that in the presence of higher physical risk with respect to the climate, clean energy ETFs become a more attractive investment option for investors that allocate their money to the various alternative energy investment products. As a result, the cross-sectional dispersion of clean energy ETFs tends to increase. Our results are in line with those of relevant studies such as @gabriel2024 who claimed that in the event of climate policy shocks, clean energy assets could serve the role of hedging instruments.

### 2025-03-24 alt_energy_herding.tex
finalising comments

We observe several periods of herding behaviour as reflected in the
troughs in Figure~\ref{fig-rolling_window}. The most prominent cases of
herding occur between March and May of 2020 followed by several
instances of herding in the period that extends from March through April
of 2017 and the period of February-March of 2023. On the other side, we
derive significant moments of anti-herding behaviour in the clean energy
ETFs by observing the spikes in Figure~\ref{fig-rolling_window}. Cross
sectional dispersion appears to increase with respect to market-wide
returns which is a sign of anti-herding behaviour on behalf of investors
around December of 2016 and later during September of 2022.

@@

The results from the Probit model are reported in
Table~\ref{tbl-probit_analysis}, where only the physical risk index
significantly decreases the probability of herding.\footnote{It should
  be noted that due to availability issues the probit analysis ends in
  December of 2023.} In other words, climate risks is good news for
clean energy stocks or firms resulting in anti-herding behaviour. This
implies that in the presence of higher physical risk with respect to the
climate, clean energy ETFs become a more attractive investment option
for investors that allocate their money to the various alternative
energy investment products. As a result, the cross-sectional dispersion
of clean energy ETFs tends to increase. Our results are in line with
those of rrelevant studies such as Gabriel \& Pinho (2024) who claimed
that in the event of climate policy shocks, clean energy assets could
serve the role of hedging instruments.

>>>>

We observe several periods of herding behaviour as reflected in the
troughs in Figure~\ref{fig-rolling_window}. The most prominent cases of
herding occur between March and May of 2020 followed by several
instances of herding in the period that extends from March through April
of 2017 (when \(\gamma_2\) averaged -45.5) and the period of
February-March of 2023 (when \(\gamma_2\) averaged -7.68).We observe
significant herding in the onset of the COVID-19 crisis 2020, which was
short lived as market adapted. The rest of the Covid period was in the
main characterised by anti-herding behaviour. \citet{ghorbel2023} and
\citet{dhall2020} found similar results. Lastly, similar to
\citet{mohamad2024} we observe no herding behaviour related to the
Russia-Ukraine war. \citet{mohamad2024} highlights the importance of
context in understanding the link between herding and market events. On
the other side, we derive significant moments of anti-herding behaviour
in the clean energy ETFs by observing the spikes in
Figure~\ref{fig-rolling_window}. Cross sectional dispersion appears to
increase with respect to market-wide returns which is a sign of
anti-herding behaviour on behalf of investors around December of 2016
and later during September of 2022.

@@

The results from the Probit model are reported in
Table~\ref{tbl-probit_analysis}, where only the physical risk index
significantly decreases the probability of herding.\footnote{It should
  be noted that due to availability issues the probit analysis ends in
  December of 2023.} In other words, climate risks is good news for
clean energy stocks or firms resulting in anti-herding behaviour. This
implies that in the presence of higher physical risk with respect to the
climate, clean energy ETFs become a more attractive investment option
for investors that allocate their money to the various alternative
energy investment products. As a result, the cross-sectional dispersion
of clean energy ETFs tends to increase. Our results are in line with
those of relevant studies such as \citet{gabriel2024} who claimed that
in the event of climate policy shocks, clean energy assets could serve
the role of hedging instruments.
